FoRTE baseline

### 2019-07-22 analysis/paper/paper.Rmd
Add observations, modify other analyses, add results text

```{r summary-ts-plot, fig.cap = summary_ts_cap, fig.dim = c(10, 10)}
summary_ts_cap <- paste(
  htmlfig(),
  "ED2 plot-level predictions of",
  "gross (GPP) and net (NPP) primary productivity,",
  "aboveground biomass (AGB),",
  "total leaf area index (LAI),",
  "and Shannon diversity index (of plant functional types)",
  "by model configuration.",
  "The solid line is the ensemble mean.",
  "Black dot with error bars is the mean and min/max value",
  "from Hardiman et al. (2013)."
)
readd(summary_ts_plot)
```

@@

Model projections of gross and net primary productivity, aboveground biomass, leaf area index, and functional diversity varied with both parameter value and model structure (Figure 2).
The ensemble means of all model configurations exhibited a similar trajectory of rapid growth in the first 15-20 years followed by a gradual decline throughout the rest of the simulation (with individual ensemble members sometimes undergoing sudden collapse in specific years).
However, the average rate of decline varied by model configuration, particularly the crown model:
Compared to models with a "closed" canopy (i.e. complete shading; no horizontal competition), models with a "finite" canopy predicted slightly faster decline in net primary productivity and functional diversity.
This decline was most severe in configurations that combined the finite canopy and two-stream radiative transfer; in these configurations, a disproportionately large number of ensembles experienced complete ecosystem collapse over the course of the simulation, and the overwhelming fraction of ensemble members predicted near-zero Shannon diversity after 30 years.
Besides this specific configuration, which consistently under-predicted observed net primary productivity at UMBS, the remaining model configurations had ensemble mean net primary productivity values that were very close to the mean observed value from Hardiman et al. (2013).
Moreover, the ensemble spread of net primary productivity from these configurations was very similar to the uncertainty in the observations, though the distribution was relatively balanced for model predictions but skewed positive for the observations.

Patterns in leaf area index were somewhat distinct from patterns in productivity and diversity.
While model configurations with finite canopy and two-stream radiative transfer again predicted the lowest leaf area index on average, model configurations with finite canopy and multiple-scatter predicted the _highest_ leaf area index on average.
The latter configurations also had the largest number of ensemble members that fell within the observed distribution of leaf area index; meanwhile, every model configuration predicted an ensemble mean leaf area index at the end of the simulation that was significantly below the observation from Hardiman et al. (2013).

@@

```{r pairs-time, fig.cap = pairs_time_cap, fig.dim = c(6, 6)}
pairs_time_cap <- paste(
  htmlfig(),
  "Time-averaged NPP vs. LAI, with observation (in black)",
  "and linear regression, by model type."
)
readd(pairs_time_averaged)
```

>>>>

```{r summary-ts-plot, fig.cap = summary_ts_cap, fig.dim = c(10, 10)}
summary_ts_cap <- paste(
  htmlfig(),
  "ED2 plot-level predictions of",
  "gross (GPP) and net (NPP) primary productivity,",
  "aboveground biomass (AGB),",
  "total leaf area index (LAI),",
  "and Shannon diversity index (of plant functional types)",
  "by model configuration.",
  "The solid line is the ensemble mean.",
  "The dashed line is the 80% confidence interval.",
  "Black dot with error bars is the mean and min/max value",
  "from Hardiman et al. (2013)."
)
readd(summary_ts_plot)
```

@@

Model projections of gross and net primary productivity, aboveground biomass, leaf area index, and functional diversity varied with both parameter value and model structure (Figure 2).
The ensemble means of all model configurations exhibited a similar trajectory of rapid growth in the first 15-20 years followed by a gradual decline throughout the rest of the simulation (with individual ensemble members sometimes undergoing sudden collapse in specific years).
However, the average rate of decline varied by model configuration.
Compared to models with a "closed" canopy (i.e. complete shading; no horizontal competition), models with a "finite" canopy predicted faster decline in net primary productivity and functional diversity.
This decline was most severe in configurations that combined the finite canopy and two-stream radiative transfer; in these configurations, a disproportionately large number of ensembles experienced complete ecosystem collapse over the course of the simulation, and the overwhelming fraction of ensemble members predicted near-zero Shannon diversity after 30 years. <!-- TODO Update this sentence -- the NPP is just super low -->
Besides this specific configuration, which consistently under-predicted observed net primary productivity at UMBS, the remaining model configurations had ensemble mean net primary productivity values that were very close to the values observed at UMBS.

Patterns in leaf area index were somewhat distinct from patterns in productivity and diversity.
While model configurations with finite canopy and two-stream radiative transfer again predicted the lowest leaf area index on average, model configurations with finite canopy and multiple-scatter predicted the _highest_ leaf area index on average (though this was skewed by a relatively small number of extremely high-LAI simulations).
The latter configurations also had the largest number of ensemble members that fell within the observed distribution of leaf area index; meanwhile, every model configuration predicted an ensemble mean leaf area index at the end of the simulation that was significantly below the UMBS observations.

```{r pairs-time, fig.cap = pairs_time_cap, fig.dim = c(8, 8)}
pairs_time_cap <- paste(
  htmlfig(),
  "Post-1975 growing season averaged NPP vs. LAI, with observation (in black)",
  "and linear regression, by model type."
)
readd(pairs_time_averaged)
```

In most simulations, the leaf area index was usually too low relative for a given level of net primary productivity, but the relationship between these two variables varied with model configuration (Figure 3).
The crown model (closed vs. finite) had the strongest effect: Compared to the simulations with "closed" crowns, simulations with finite canopy radius generally had lower net primary productivity for the same leaf area index.
Only a few simulations matched _both_ the observed leaf area index and net primary productivity, and all of them had the finite canopy radius configuration.

@@
